%% start of file `template-zh.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
%\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}

\usepackage[scale=0.8]{geometry}
\recomputelengths
\recomputecvlengths
%\setlength{\hintscolumnwidth}{3cm}

%====================
% Personal information
%====================
\firstname{Juanjie}
\familyname{Xi}
%\title{Curriculum Vitae}
%\address{xxxxxxxxxx}{xxxxxxxxxx}
\mobile{070-4497-3481}
%\phone{xxxxxxxxxx}
%\fax{xxxxxxxxxx}
\email{strangemk3@gmail.com}
%\homepage{www.pm525.com}
%\extrainfo{附加信息 (可选项)}
%\photo[64pt][0.4pt]{picture}
\quote{%Summary\newline{}
\small
\begin{itemize}
\item 15+yrs experience in Software Development Life Cycle
\item Engineering Manager of 2 groups up to 20 people
\item Extensive in-depth Linux experience
\item Experienced in design, operate and maintain high performance systems
\item Good knowledge of Data Structures, Algorithms and Design Patterns
\item Strong domain knowledge in email industry
\item Trilingual, speak Chinese, Japanese and English
%\item Experience in the game industry
\end{itemize}
\normalsize
}

%====================
% Content
%====================
\begin{document}
\begin{CJK}{UTF8}{gbsn} % Chinese
%\begin{CJK}{UTF8}{ipxm} % Japanese
\maketitle

%\section{Experience}
%\cventry{Aug 2017 - Present}{Manager}{Rakuten}{Tokyo}{Japan}{}
%\cventry{Jan 2011 - Jul 2017}{Technical leader}{HP}{Shanghai/Tokyo}{}{}
%\cventry{Oct 2007 - Dec 2010}{Programmer}{From Software}{Tokyo}{Japan}{}
%\cventry{Jul 2004 - Aug 2007}{Software Engineer}{Venus Software}{Shanghai}{China}{}

\section{Experience}
\cventry{Jan 2020 - Present}{Rakuten}{Engineering manager}{}{}{
In charge of Rakuten multiple channels messaging delivery platform. Lead 2 groups up to 20 member to provide messaging delivery service for Emails, Line and Viber. This platform is used by more than 80 organizations in Rakuten.
\begin{itemize}
\item Take the final responsibility of the group and product
\item Build group vision and roadmap to provide competitive products in email delivery industry
\item Manage the team by goal setting, evaluation, 1on1, training, and mentoring
\item Continue to improve the development process and optimize the technical stack
\item Participate technical discussions and reviews
\item Communicate with clients to gather requirements and provide supports
\item Delivered the next generation email delivery engine after five years of development, which have better interface, fairly scheduling algorithm, easily trackable and scalable
\item Build one team into two groups
%\item Achievements include "Refresh MTA infrastructures", "New delivery platform provide better interface, triple performance", "Email security projects", etc...
%\item 人事Goal setting, evaluation, 1on1, hiring mentoring, training
%\item 军事Paperworks labor, techniques
%\item 内政 team building, organization, improvement
%\item 外交 communication, ticket, trouble
\end{itemize}
}

\cventry{Aug 2017 - Dec 2019}{Rakuten}{Software engineer}{}{}{
Working on Rakuten Email delivery platform, which delivers almost all emails from Rakuten to customers. More than 3 billion of emails have been delivered every month. This platform is the most significant email sender in Japan email market.
\begin{itemize}
\item Lead the development of the next generation email delivery engine with the advanced scheduling algorithm.
\item Designed and created a fully automated pipeline for building new MTA servers. Including server creation, middleware setup, testing and service-in.
\item Designed the log streaming system to support the huge amount of logs produced by email delivery platform.
\end{itemize}
}

\cventry{Jan 2011 - Jul 2017}{Hewlette Packard}{Software engineer}{}{}{
Maintain a large scale email service for a top Japanese mobile service provider. It includes developing new features, expanding services, supporting new clients and bug fixing.
\begin{itemize}
\item Lead the project development of max 10 people group using c/c++ and Perl.
\item Developed an in-memory caching middleware for IMAP which made the response of IMAP session 10x faster than before.
\item Developed an SMTP login control system based on Nginx which serves 60 million of users. This system makes switching MTA backend possible, significantly reduced the difficulties of email system.
\item Discuss requirement with business team, do technical investigation and POC, design specifications and communicates with development team.
\end{itemize}
}

\cventry{Oct 2007 - Dec 2010}{From software}{Game programmer}{}{}{
\begin{itemize}
\item Developed two game titles in Nintendo DS and Sony PSP using C++ and hardware SDK
\item Built and maintained serials of internal game development tools, including 3D modeling, resource management and gaming event maker
\end{itemize}
}
\cventry{Jul 2004 - Sept 2007}{Venus software}{Software engineer}{}{}{
\begin{itemize}
\item Developed various types of applications. Such as Java, Networking, Multithreading, C++ and GUI applications
\end{itemize}
}

%\clearpage

\section{Skills}
\cvcomputer{Languages}{C++, Perl, Python, Java}{DB}{MySQL, SQLite}
\cvcomputer{Platforms}{Gentoo, Debian, Redhat, FreeBSD, Nginx, Redis, k8s, Kafka, Postfix}{Tools}{vim, clang, git, Trac, Jira, binutils}

\section{Education}
\cventry{2000 - 2004}{University of Shanghai for Science and Technology}{Building Environment and Equipment Engineering}{Bachelor}{}{}

\section{Certifications}
%\cvitemwithcomment{LPIC Level1}{}{December 2009}
%\cvitemwithcomment{LPIC Level2}{}{March 2013}
\cvitemwithcomment{}{Senior Programmer Certificate}{October 2006}
\cvitemwithcomment{}{JLPT 1}{August 2007}

\section{Tests}
\cvline{TOEIC}{840}

%\section{Interestsaa}
%\cvitem{hobby 1}{Descripci\'on}
%
%\section{Conocimientos de computaci\'on}
%\cvdoubleitem{categor\'ia 1}{XXX, YYY, ZZZ}{categor\'ia 4}{XXX, YYY, ZZZ}

\section{Personal projects}
\cvlistitem{Running a personal Email service}
\cvlistitem{Maintained a bbs site for more than 10 years. At the peak time, it has more than 0.2 million registered users}

\section{Info}
%\cvline{Birth}{\small Aug 28th, 1982 (Shanghai)\normalsize}
\cvline{LinkedIn}{\small \url{https://www.linkedin.com/in/xijuanjie}\normalsize}
\cvline{Github}{\small \url{https://github.com/strangemk2}\normalsize}
%\cvline{Blog}{\small \url{<Link to profile>}\normalsize}
%\cvline{Skype}{\small <skype>\normalsize}

%\section{Interests}
%\cvlistdoubleitem{Cycling}{Go game}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}

%\clearpage

\clearpage
\end{CJK}
\end{document}
